\documentclass[letter]{article}
\usepackage[hmargin=0.75in, vmargin=0.75in]{geometry}

\usepackage{hyperref,url}
\usepackage[backend=biber,style=ieee,defernumbers=true]{biblatex}
\addbibresource{../publications.bib}
\DeclareNameFormat{author}{%
  \ifthenelse{\equal{#1}{Amos}}%
    {\textbf{\ifblank{#4}{}{#4\space}#1}}%
    {\ifblank{#4}{}{#4\space}#1}%
  \ifthenelse{\value{listcount}=1 \AND \value{liststop}=2}%
    {\space and\space}
    {\ifthenelse{\value{listcount}<\value{liststop}}%
      {\addcomma\space}
      {}
    }
}

\usepackage{fancyhdr}\pagestyle{fancy}\usepackage{lastpage}
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\cfoot{Page \thepage\ of \pageref{LastPage}}

\usepackage{enumitem}\setlist{nolistsep}
\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}\setlength{\parsep}{0pt}
\setlength\parindent{0pt}\setlength{\topskip}{0pt}

\usepackage{titlesec}
\titleformat*{\section}{\huge}

\usepackage{hyphenat}\hyphenation{Mathematica}

\begin{document}
{\huge Ghassen Telmoudi. vit\ae.} \hfill
{Phone.} {\small (+216) 53 98 69 75} \hspace{2mm}
{Email.} {\small \href{mailto: ghassen.telmoudi@gmail.com }{ ghassen.telmoudi@gmail.com }} \\
\url{ https://github.com/pyghassen } \hfill Generated \today.
\vspace{3mm}

\medskip

\begin{minipage}{\textwidth}
{\huge Research Interests }


  Python; Django; RESTful APIs; Linux.
  \bigskip

\end{minipage}\medskip

\begin{minipage}{\textwidth}
{\huge Education }


  
    {\large ISET } \hfill  \\
    Bachelor's Degree, Computer Science.\hfill {\it }
    \bigskip
  

\end{minipage}\medskip

\begin{minipage}{\textwidth}
{\huge Teaching Experience }


  \begin{itemize}
    
      \item
        Undergraduate TA.
        {\bf CS 2114, Software Design and Data Structures}.
        Virginia Tech.
        {\it January 2013--May 2013}.
    
  \end{itemize}

\end{minipage}\medskip

\begin{minipage}{\textwidth}
{\huge Publications }


  \nocite{*}
  \bigskip{\Large Conference Proceedings.}
  \printbibliography[heading=none,type=inproceedings,prefixnumbers=C]
  \end{minipage}
  \begin{minipage}{\textwidth}
  \bigskip{\Large Journal Articles.}
  \printbibliography[
    heading=none,type=article,keyword=journal,
    resetnumbers=true,prefixnumbers=J
  ]
  \bigskip{\Large Magazine Articles.}
  \printbibliography[
    heading=none,type=article,keyword=magazine,
    resetnumbers=true,prefixnumbers=M
  ]
  \bigskip


\end{minipage}\medskip

\begin{minipage}{\textwidth}
{\huge Industry Experience }


  
    {\large Rosafi Holding } \hfill Tunis, Tunisia \\
    Software Developer\hfill {\it February 2012--Present}\begin{itemize}
      
        \item {\bf Research Area}: Distributed Systems
      
        \item Built and released {\it Spindle}, an open source web analytics processing engine with {\bf Scala}, {\bf Spark}, {\bf Spray}, and {\bf Parquet} on {\bf HDFS}.
      
        \item Spindle is available on GitHub at \url{http://github.com/adobe-research/spindle}.
      
      \end{itemize}\end{minipage}
    \begin{minipage}{\textwidth}
    \bigskip
  
    {\large Snowplow Analytics } \hfill London, United Kingdom (Remote) \\
    Software Winter Intern\hfill {\it December 2013--January 2014}\begin{itemize}
      
        \item Open-source {\bf Scala} development with a startup on the Snowplow analytics platform, available at \url{http://github.com/snowplow/snowplow}.
      
        \item Developed a new server using {\bf Spray} and {\bf Actors} to store {\bf Apache Thrift} events on {\bf Amazon Kinesis}.
      
        \item Completed project ahead of schedule, and also helped port Snowplow's Scala enrichment process to Kinesis.
      
      \end{itemize}\end{minipage}
    \begin{minipage}{\textwidth}
    \bigskip
  
    {\large Qualcomm } \hfill San Diego, California \\
    Source Integrity Team Software Intern\hfill {\it May 2013--August 2013}\begin{itemize}
      
        \item Developed an XML modification {\bf web application} for fuzz vector generation. Implemented with client-side {\bf HTML} and {\bf js}, using {\bf D3} for graphics and {\bf Handlebars} for templating.
      
        \item Developed an XML-based grammar translator in {\bf C++} with the {\bf Xerces} XML parser in {\bf Linux}. Reimplemented in {\bf Python} using the {\bf ElementTree} XML API for sophisticated analysis and tree transformations.
      
      \end{itemize}\end{minipage}
    \begin{minipage}{\textwidth}
    \bigskip
  
    {\large Phoenix Integration } \hfill Blacksburg, Virginia \\
    Software Engineer Intern\hfill {\it May 2012--August 2012}\begin{itemize}
      
        \item Developed industry software in {\bf VC++}, {\bf VC\#}, {\bf Java}, and {\bf Tomcat}.
      
        \item Improved the testing ({\bf JUnit} and {\bf NUnit}) and installation ({\bf Ant}, {\bf InstallShield}, and {\bf Make}) frameworks.
      
        \item Integrated a new licensing mode into CenterLink, a grid computing application, using {\bf FLEXlm} and {\bf Java}.
      
      \end{itemize}\end{minipage}
    \begin{minipage}{\textwidth}
    \bigskip
  
    {\large Sunapsys } \hfill Vinton, Virginia \\
    Network Administrator Intern\hfill {\it January 2011--August 2011}\begin{itemize}
      
        \item Internship in high school to replace Windows domain, mail, DHCP, and DNS servers with virtual {\bf Linux} servers using {\bf KVM} and {\bf virsh}.
      
        \item Migrated the office's computers to the Linux servers.
      
        \item Created {\bf Bash} scripts for incremental backups with rsync and hard links.
      
      \end{itemize}\end{minipage}
    \begin{minipage}{\textwidth}
    \bigskip
  

\end{minipage}\medskip

\begin{minipage}{\textwidth}
{\huge Projects }


  
    {\large GitHub Portfolio -- \url{ http://github.com/bamos } }
    \begin{itemize}
      
        \item Hosts code samples, original source code, and patches for open source projects.
      
        \item 25 original repositories, 5 forked repositories.
      
    \end{itemize}
    \bigskip
  
    {\large Personal Blog and Website -- \url{ http://bamos.io } }
    \begin{itemize}
      
        \item Hosted on GitHub Pages. Uses {\bf Markdown} for posts and {\bf Jekyll} for static HTML generation.
      
        \item {\bf 42 posts} across the following tags, listed by highest frequency.
      
        \item Python, Bash, Linux, LaTeX, Fortran, Android, Scala, News, JavaScript, Zsh, C++, OpenMP, Lua, Make, Mathematica, mpv
      
    \end{itemize}
    \bigskip
  

\end{minipage}\medskip

\begin{minipage}{\textwidth}
{\huge Skills }


  \begin{itemize}
    
      \item { \bf Preference. } Arch Linux/Mac, vim/emacs, git/Make/sbt
    
      \item { \bf Languages. } Akka**, Bash**, C/C++**, C\#*, Fortran**, HTML/CSS*, \LaTeX**, Java**, JavaScript**, {\it Mathematica}**, Make***, PHP*, Python***, R*, Scala***
    
      \item { \bf Systems. } Android**, Linux***, Mac***
    
      \item { \bf Rankings. } 1/10* -- 3/10** -- 5/10*** -- 7/10****
    
  \end{itemize}
  \bigskip

\end{minipage}\medskip

\begin{minipage}{\textwidth}
{\huge Honors \& Awards }


  \begin{itemize}
    
      \item Phi Beta Kappa Honor Society, Inducted 2014
      
    
      \item 1st Place Capstone Award, Virginia Tech Computer Science, 2014
      
    
      \item David Heilman Research Award, Virginia Tech Computer Science, 2014
      
        \begin{itemize}
          \item Given to the Computer Science student with the most outstanding research experience.
        \end{itemize}
      
    
      \item Senior Scholar Award, Virginia Tech Computer Science, 2014
      
        \begin{itemize}
          \item Given to the senior in Computer Science with the most outstanding academic record.
        \end{itemize}
      
    
      \item ACC Meeting of the Minds Undergraduate Research Conference, 2014
      
    
      \item Honorable Mention, CRA Outstanding Undergraduate Researcher Award, 2014
      
        \begin{itemize}
          \item 1 of 15 North American males awarded honorable mention for exemplary computer science research.
        \end{itemize}
      
    
      \item Qualstar Award, Qualcomm, 2013
      
    
      \item Pi Mu Epsilon Honor Society, Inducted 2013
      
    
      \item Benjamin F. Bock Merit Scholarship, Virginia Tech Engineering, 2013--2014
      
    
      \item Sophomore Scholar Award, Virginia Tech Computer Science, 2013
      
    
      \item University Honors, Virginia Tech, 2012--2014
      
    
      \item Intelligence Community Center of Academic Excellence Scholar, Virginia Tech, 2012--2014
      
        \begin{itemize}
          \item Merit-based scholarship providing a cyber-security research fellowship.
        \end{itemize}
      
    
      \item Dean's List with Distinction, Virginia Tech, 2011--2014
      
    
      \item Engineering Merit Scholarship, Roanoke County Public Schools Education Foundation, 2011
      
        \begin{itemize}
          \item Merit-based scholarship presented annually to one student in the graduating Engineering class.
        \end{itemize}
      
    
      \item Papa John's Merit Scholarship, 2011
      
    
      \item Gay B. Shober Memorial Merit Scholarship, Roanoke County Federal Credit Union, 2011
      
    
      \item Pamplin Leader Scholarship, Virginia Tech, 2011
      
        \begin{itemize}
          \item Merit-based scholarship presented to one student from each public high school in Virginia.
        \end{itemize}
      
    
      \item I. Luck Gravett Memorial Merit Scholarship, Scottish Rite of Freemasonry, 2011
      
    
      \item Salem--Roanoke County Chamber of Commerce Merit Scholarship, 2011
      
    
  \end{itemize}
  \bigskip

\end{minipage}\medskip

\begin{minipage}{\textwidth}
{\huge Activities }


  \begin{itemize}
    
      \item Honors Residential College, Virginia Tech, 2013--2014
    
      \item Hokies Pep Band, Virginia Tech, 2012--2013
    
      \item Computer Science Community Service, Virginia Tech, 2012
    
      \item Symphony Band, Virginia Tech, 2011--2012
    
      \item Linux and Unix Users Group, Virginia Tech, 2011--2012
    
      \item Galileo Living--Learning Community, Virginia Tech, 2011--2012
    
  \end{itemize}
  \bigskip

\end{minipage}

\end{document}